Automating Verification of MPC Security

### 2023-06-06 popl24/metalang.tex
checkpoint

$$
\begin{array}{rcl@{\hspace{8mm}}r}
b &\in& \{ \etrue, \efalse \} \\
w &\in& \mathrm{String} \\ 
\cid &\in& \mathrm{Clients} \qquad  (\mathrm{Clients} \subset \mathbb{N} \text{\ in\ this\ presentation})\\[2mm]
\bop &\in& \{ \eand, \eor, \exor \} \\[2mm]
\be &::=& b \mid \flip{\cid}{w} \mid \secret{\cid}{w} \mid \view{\cid}{w} \mid \oracle{w} \mid & \textit{boolean expressions}\\
& &  \enot\ \be \mid \be\ \bop\ \be \mid \select{\be}{\be}{\be} \\[2mm]
\instr &::=& \eassign{\view{\cid}{w}}{\be} \mid \eassign{\view{\cid}{w}}{\OT{\be}{\be}{\be}} & \textit{view assignments} \\[2mm]
\prog &::=& \instr \mid \instr; \prog & \textit{protocols}
\end{array}
$$

\begin{eqnarray*}
\lcod{\store, \etrue}{\cid} &=& \etrue\\
\lcod{\store, \efalse}{\cid} &=& \efalse\\
\lcod{\store, \flip{\cid}{w}}{\cid} &=& \store(\flip{\cid}{w})\\
\lcod{\store, \secret{\cid}{w}}{\cid} &=& \store(\secret{\cid}{w})\\
\lcod{\store, \view{\cid}{w}}{\cid} &=& \store(\view{\cid}{w})\\
\lcod{\store, \oracle{w}}{\cid} &=& \store(\oracle{w})\\
\lcod{\store, \enot\ \be}{\cid} &=& \cod{\enot\ \lcod{\store,\be}{\cid}}\\
\lcod{\store, \be_1\ \mathit{binop}\ \be_2}{\cid} &=&
    \cod{\lcod{\store,\be_1}{\cid}\ \mathit{binop}\ \lcod{\store,\be_2}{\cid}}\\
\lcod{\store, \select{\be_1}{\be_2}{\be_3}}{\cid} &=&
             \begin{cases}
                \lcod{\store,\be_2}{\cid} & \text{if\ } \lcod{\store,\be_1}{\cid}\\
                \lcod{\store,\be_3}{\cid} & \text{otherwise}
             \end{cases}
\end{eqnarray*}

\begin{mathpar}
  (\store, \eassign{\view{\cid}{w}}{\be};\prog) \redx (\extend{\store}{\view{\cid}{w}}{\lcod{\store,\be}{\cid}}, \prog)

  \inferrule
  {b = \text{if\ } \lcod{\store,\be_1}{\cid}  \text{\ then\ } \lcod{\store,\be_2}{\cid'} \text{\ else\ } \lcod{\store,\be_3}{\cid'}}
      {(\store, \eassign{\view{\cid}{w}}{\OT{\be_1}{\be_2}{\be_3}};\prog) \redx (\extend{\store}{\view{\cid}{w}}{b}, \prog)}
\end{mathpar}

$$
\begin{array}{rcl@{\hspace{8mm}}r}
\flab &\in& \mathrm{Field}\\
x &\in& \mathrm{EVar}\\
f &\in& \mathrm{FName}\\[2mm]
e &::=& b \mid \flip{e}{e} \mid \secret{e}{e} \mid \view{e}{e} \mid \oracle{e} \mid \enot\ e \mid e\ \eand\ e \mid e\ \exor\ e \mid & \textit{expressions}\\[0mm]
& & \select{e}{e}{e} \mid 
\send{\view{e}{e}}{e} \mid \send{\view{e}{e}}{\OT{e}{e}{e}} \mid e;e \mid \\[0mm]
& & x \mid \elet{x}{e}{e} \mid f(e,\ldots,e) \mid \{ \flab = e; \ldots; \flab = e \}
\mid e.\flab \mid e\ttt{||}e \mid (e) \\[2mm]
v &::=& w \mid b \mid \cid \mid \{ \flab = v;\ldots;\flab = v \} 
\mid (\,) & \textit{values}\\[2mm]
{fn} &::=& f(x,\ldots,x) \{ e \} & \textit{functions}
\end{array}
$$

@@

>>>>

$$
\begin{array}{rcl@{\hspace{8mm}}r}
\flab &\in& \mathrm{Field}\\
x &\in& \mathrm{EVar}\\
f &\in& \mathrm{FName}\\[2mm]
e &::=& b \mid \flip{e}{e} \mid \secret{e}{e} \mid \view{e}{e} \mid \oracle{e} \mid \enot\ e \mid e\ \eand\ e \mid e\ \exor\ e \mid & \textit{expressions}\\[0mm]
& & \select{e}{e}{e} \mid 
\send{\view{e}{e}}{e} \mid \send{\view{e}{e}}{\OT{e}{e}{e}} \mid e;e \mid \\[0mm]
& & x \mid \elet{x}{e}{e} \mid f(e,\ldots,e) \mid \{ \flab = e; \ldots; \flab = e \}
\mid e.\flab \mid e\ttt{||}e \mid (e) \\[2mm]
v &::=& w \mid \cid \mid \be \mid \{ \flab = v;\ldots;\flab = v \} 
\mid (\,) & \textit{values}\\[2mm]
{fn} &::=& f(x,\ldots,x) \{ e \} & \textit{functions}
\end{array}
$$

@@

\begin{verbatimtab}
andgg(g, wla, wlb, wlc, wva, wvb) {
andgate(g, wla, wlb, wlc);
evalgate(g, wva, wvb)
}
\end{verbatimtab}

\begin{lemma}[Input Encoding]
Assume given the following evaluation relation:
$$
\config{\prog_1}{E[\ttt{encode}(w,v_1,v_2)]} \redxs \config{\prog_1;\prog_2}{E[v]}
$$
If there exists gate identifiers $g_1, g_2$ such that:
\begin{enumerate}
  \item $g_1 \ne g_2 \wedge g_1,g_2 \not\in \gates(\prog_1)$
  \item $\owl(\prog_1,v_1,g_1) \wedge \owl(\prog_1,v_2,g_2)$
  \item $\gNIMO(\prog_1,v.\ttt{wv1},g_1) \wedge \gNIMO(\prog_1,v.\ttt{wv2},g_2)$
\end{enumerate}
then:
\begin{enumerate}
\item $g_1,g_2 \in  \gates(\prog_2)$
\item $\gNIMO(\prog_1;\prog_2,v.\ttt{wv1},g_1) \wedge \gNIMO(\prog_1;\prog_2,v.\ttt{wv2},g_2)$
\item $$(\margd{\progd(\prog_1;\prog_2)}{\iov(\prog_1)}) * (\margd{\progd(\prog_1;\prog_2)}{\iov(\prog_2)})$$
\end{enumerate}
\end{lemma}

\begin{lemma}[Composition ($\eand$)]
Assume given the following evaluation relation:
$$
\config{\prog_1}{E[\ttt{andgg}(g,v_1,\ldots,v_5)]} \redxs \config{\prog_1;\prog_2}{E[v_6]}
$$
If there exist gate identifiers $g_1, g_2$ such that:
\begin{enumerate}
  \item $g_1 \ne g_2 \ne g \wedge g_1,g_2 \in \gates(\prog_1) \wedge g \not\in \gates(\prog_1)$
  \item $\owl(\prog_1,v_1,g_1) \wedge \owl(\prog_1,v_2,g_2) \wedge \owl(\prog_1,v_3,g)$
  \item $\gNIMO(\prog_1,v_4,g_1) \wedge \gNIMO(\prog_1,v_5,g_2)$
\end{enumerate}
then:
\begin{enumerate}
  \item $g \in \gates(\prog_2)$
  \item $\gNIMO(\prog_1;\prog_2,v_6,g)$
  \item $(\margd{\progd(\prog_1;\prog_2)}{\iov(\prog_1)}) * (\margd{\progd(\prog_1;\prog_2)}{\iov(\prog_2)})$
\end{enumerate}
\end{lemma}

\begin{lemma}[Decoding]
Assume given the following evaluation relation:
$$
\config{\prog_1}{E[\ttt{decoder}(v_1,v_2)]} \redxs \config{\prog_1;\prog_2}{E[\be]}
$$
If there exists gate identifier $g \in \gates(\prog_1)$ such that:
\begin{enumerate}
  \item $\owl(\prog_1,v_1,g)$
  \item $\gNIMO(\prog_1,v_2,g)$
\end{enumerate}
Then $\NIMO(\prog_1;\prog_2;\eassign{x}{\be})$.
\end{lemma}
